Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-18 manuscript/extended_supplemental_material.Rnw
duplicate supplemental material for cutting
ignore more filex, change extended supplement path

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.6\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE,cache.path="supplemental_cache/")
opts_chunk$set(fig.path="supplemental_figure/")
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("scales")
library("gridExtra")
library("ape")
library("ggtree")
library("RSQLite")
library("topGO")
library("org.Hs.eg.db")
library("magrittr")
library("tidyr")

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.6\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE,cache.path="extended_supplemental_cache/")
opts_chunk$set(fig.path="extended_supplemental_figure/")
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("scales")
library("gridExtra")
library("ape")
library("ggtree")
library("RSQLite")
library("topGO")
library("org.Hs.eg.db")
library("magrittr")
library("tidyr")
